---
title: "Extract pesticide concentration at sample locations"
output:
        prettydoc::html_pretty:
                theme: cayman
                highlight: github
author: Jonathan Jupke
---


**Purpose**     
In this script I extract the pesticide concentration for all 162 pesticides for the samples from the UK biomonitoring.     
**Data files**    
**Date**    
- script created:     2021.09.07     
- script last modified: `r Sys.Date()`    

***    

```{r dependencies, warning = FALSE, message = FALSE}
library(data.table)
library(dplyr)
library(magrittr)
library(purrr)
library(terra)
library(tidyr)
library(sf)
library(stringr)
```

First I wrap the extraction in a function. 
```{r}
#@Param X: the name of the raster to extract from 
#@Param y: the sampling sites 

extract_raster <- function(x,y){
        #- get the pesticide name 
        pesticide.name <-
                as.character(x) |> 
                str_extract(pattern = "data/.*\\.tif$") |> 
                str_remove(pattern = "data/") |> 
                str_remove(pattern = "\\.tif")
        #- read in the raster 
        x <- rast(x)

        #- extract values 
        z <- terra::extract(x = x, 
                            y = y)
        z <- data.table(site_id = y$site_id,
                        placeholder = z[, 2])
        names(z)[2] <- pesticide.name
        z
        
}
```

Load the biomonitoring data and extract sites. 
```{r}
biodata    <-  readRDS("~/01_Uni/my_papers/2021_02_getreal_mzb_paper/freshwater-typologies-mzb/data/original data/monitoring_uk/2021-09-03_final.rds")
sites <- 
        biodata[year > 2014] |> 
        unique(by = "site_id") |> 
        st_as_sf(coords = c("x.coord", "y.coord"), crs = biodata$EPSG[1])
sites %<>% select(site_id)
sites %<>% vect()

```

Compile a list of all the pesticide rasters.
```{r}
pesticide.folder <- "E://Arbeit/Data/UK_Pesticide/UK_Pesticide/CEH Land Cover Plus Pesticides England Scotland Wales/data/"
pesticide.files <- fs::dir_ls(pesticide.folder)
```

Extract values.
```{r}
site_w_pesticides <- 
        map(.x = pesticide.files,
            .f = ~ extract_raster(x = .x, y = sites)) |>
        reduce(left_join, by = "site_id")
```

I would also like to have this table in long format. 
```{r}
pesticides.long <- pivot_longer(site_w_pesticides, cols = !site_id, names_to = "compound", values_to = "amount")
```
Missing values (NaN) correspond to cells where the pesticide is not applied (at least according to the model). 
I will set them to zero. 
```{r}
pesticides.long[which(is.nan(pesticides.long$amount)), "amount"] <- 0
```
And now use this updated data set to recreated a new wide data set. 
```{r}
pesticides.wide <- pivot_wider(data = pesticides.long, id_cols = "site_id", names_from = "compound", values_from = "amount")
```

Save data as list. 
```{r}
out.ls <- list(wide = pesticides.wide, 
               long = pesticides.long)
saveRDS(object = out.ls, 
        file = paste0("../data/", Sys.Date(), "_sites_w_pesticides.rds"))
```


***    

```{r}
sessionInfo()
```

