---
title: "Explore pesticide data"
output:   
        prettydoc::html_pretty:
                theme: cayman
                highlight: github
author: Jonathan Jupke
---


**Purpose**     
Explore the pesticide data. The data consist of one .tif file for each of 162 pesticides.                
**Data files**    

**Date**    
- script created:  2021.09.07   
- script last modified: `r Sys.Date()`    

***    

```{r dependencies, warning=FALSE, message = FALSE}
library(data.table)
library(sf)
library(terra)
library(tmap)
tmap_mode("view")
```

Read in one of the pesticide rasters ... 
```{r}
pesticides <- rast("E://Arbeit/Data/UK_Pesticide/UK_Pesticide/CEH Land Cover Plus Pesticides England Scotland Wales/data/Acetamiprid.tif")
biodata    <-  readRDS("~/01_Uni/my_papers/2021_02_getreal_mzb_paper/freshwater-typologies-mzb/data/original data/monitoring_uk/2021-09-03_final.rds")
```

... and inspect it ... 
```{r}
pesticides
```

... and plot it. 
```{r, warn = FALSE}
tm_shape(pesticides[[1]]) + tm_raster() + tm_facets(as.layers = TRUE)
```
The first layer gives the estimated application amount (kg/yr) and the second the percentage uncertainty. 

Now I extract the sites from the UK Monitoring data and then plot both the raster and the points together. 
```{r}
sites <- biodata[year > 2014]
sites <- unique(sites, by = "site_id")
sites <- st_as_sf(sites, coords = c("x.coord", "y.coord"), crs = sites$EPSG[1])
```

```{r}
pesticides1 <- pesticides["Ace_1"]
tm_shape(pesticides1) + tm_raster() + tm_shape(sites) + tm_dots()
```

# Try to connect the two

Sample 10 random points from the samples 
```{r}
sites.2 <- sites[1:10, ]
```

Transform the subsample to the SpatVector class. 
```{r}
sites.3 <- terra::vect(sites.2)
```

```{r}
extraction <- terra::extract(
        y = sites.3, 
        x = pesticides1
        )
```

works great! 

***    

```{r}
sessionInfo()
```

